Efficiently Handling Guards in the Low Level Design of RPython's tracing JIT

### 2012-08-07 talk/vmil2012/paper.tex
some tweaks to the related work

In~\cite{Gal:2006} Gal et. al describe that in the HotpathVM they experimented
with having one generic compensation code block, like the RPython JIT, that
uses a register variable mapping to restore the interpreter state. Later this
was replaced by generating compensation code for each guard which produced a
lower overhead in their benchmarks. HotpathVM also records secondary traces
starting from failing guards that are connected directly to the original trace.
Secondary traces are compiled by first restoring the register allocator state to
the state at the side exit. The information is retrieved from a mapping stored
in the guard that maps machine level registers and stack to Java level stack
and variables.

Gal et. al~\cite{Gal:2009ux} write about how TraceMonkey uses trace stitching
to avoid th overhead of returning to the trace monitor and calling another
trace when taking a side exit. In their approach it is required to write live
values to an activation record before entering the new trace.

>>>>

Gal et. al~\cite{Gal:2006} describe that in the HotpathVM they experimented
with having one generic compensation code block, like the RPython JIT, that
uses a register variable mapping to restore the interpreter state. Later this
was replaced by generating compensation code for each guard which produced a
lower overhead in their benchmarks. HotpathVM also records secondary traces
starting from failing guards that are connected directly to the original trace.
Secondary traces are compiled by first restoring the register allocator state to
the state at the side exit. The information is retrieved from a mapping stored
in the guard that maps machine level registers and stack to Java level stack
and variables.

TraceMonkey, a tracing JIT for JavaScript, uses trace stitching
to avoid the overhead of returning to the trace monitor and calling another
trace when taking a side exit~\cite{Gal:2009ux}. In this approach it is required to write live
values to an activation record before entering the new trace.
